---
title: "Bigmac"
author: "Dr J"
date: "07/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
get an estimated demand curve for big macs

```{r}
BigM = read.csv('Book1.csv')
attach(BigM)
```



plot the data
```{r}
plot(demand, price);
```
fit a demand line to these data
```{r}
model1 = lm(price~demand)
summary(model1)
plot(demand, price)
abline(model1)
abline(h = 4.5, col='red')
```

price elasticity is the % change in quality demanded divided by the % change in price
marginal revenue of an product is the additional revenue for the sales of one additional Big Mac

MR is related to price elasticity by 
Mr = PRICE * (1 + elasticity)/elasticity

At Miley D's MR=MC
E = slope of demand at price p * (price/quantity)
```{r}
slope = model1$coefficient[2]
E = slope*4.5/3.5
MR = 4.50 * (1+E)/E
print(paste('elasticity =', round(E,2)))
print(paste('MR =', round(MR,2)))
```
profit = price - cost = 4.5- MC
```{r}
profit = price - MR
```


